The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
add lc details

### Landscape data and habitat classification

>>>>

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types, which we distilled into two broad categories: open and closed habitat types. Open habitat consisted of lichen, wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.
